Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-12-27 demystify.tex
Updates from Overleaf

  \item[Domestic Student] A student who is typically a US citizen or permanent resident (``greencard holder'').
        But sometimes it can also refer to students who did their undergrad (or MS) at a US university.

@@

For international students pursuing a PhD in the US, \textbf{F-1} is the main visa that allows a student to study full-time at an accredited institution.  Here are some key points about the F-1 visa:

@@

Most of what is written in this handbook applies to both domestic\footnote{For simplicity domestic means you did your undergrad (or MS) at a US university. Different universities might have different definitions, e.g., permanent residents or US citizens.} and international students.  However, there are some differences and benefits that domestic students should be aware of and can leverage to improve their chances of admission.
\paragraph{Standing out \autoref{sec:improve-your-chance}} There are \emph{few} domestic applications compared to international ones, i.e., domestic students are the minority (\autoref{sec:urm}) in the CS PhD application pool. Many US universities want to increase the number of domestic students in their programs (and as mentioned later, there are specific fellowships and funding for domestic students).
That makes you stand out and can help your case.

>>>>

@@

As defined in~\autoref{chap:glossary}, international students are those who would need a visa to study in the US.  In most cases, \textbf{F-1} is the main visa needed to study full-time at an accredited institution.  Here are some key points about F-1:

@@

Most of what is written in this handbook applies to both domestic\footnote{As mentioned in \autoref{chap:glossary}, domestic means you do not require a visa to study in the US.} and international students.  However, there are some differences and benefits that domestic students should be aware of and can leverage to improve their chances of admission.
\paragraph{Standing out \autoref{sec:improve-your-chance}} There are \emph{few} domestic applications compared to international ones, i.e., domestic students are the minority (\autoref{sec:urm}) in the CS PhD application pool. Many US universities want to increase the number of domestic students in their programs (and as mentioned later, there are specific fellowships and funding for domestic students).
That makes you stand out and can help your case.
